\documentclass[a4paper]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

\title{Project Technology Report}
\author{Rishiraj Bheenick, Robert Holland, Ruiao Hu, Fangyi Zhou}

\begin{document}
\maketitle

\section{Back End Language Choice}

The back end of this app is made in \texttt{node.js}. The choice has been made
for the following reasons.
\begin{enumerate}
\item
There are abundant Javascript packages available for physics engine needed for
the racing game. This smoothes the development process by a lot and there is no
need to re-invent the wheel.
\item
Javascript packages could be used in both front end and back end. The
simulation code in the front end and back end could be very similar so that
there is no need to code similar snippets in different languages.
\end{enumerate}

\section{Front End Framework Choice}

The front end of this app uses \texttt{Angular} framework.

\section{Continuous Integration}

The project uses \texttt{Travis CI} for continuous integration. After each push
to \texttt{Github}. The continuous integration service will start a build and
run tests using \texttt{npm test} after the build.

\section{Deployment}

The projects runs on \texttt{Heroku}. A webhook is set so that the latest
commit will be automatically deployed if it passes the continuous integration
test as stated in previous section.

\end{document}
